Mapping Microblogging Posts to Encyclopedia Articles

### 2011-02-22 trunk/lids/twittersearchwrap/paper/paper.tex

The implemented
system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}}
(further called Twitter Search Wrapper) is called with a query and returns a
rdf\footnote{\url{http://www.w3.org/RDF/}} document describing the most recent
twitter posts (further called tweets) matching the given query. The returned rdf
document furthermore contains a mapping of the query to Encyclopedia articles
which based on the content published by users that most recently used the query
in their posts maps to articles best describing the content of tweets related to
the query. An overview of the System Architecture is given in Figure
\ref{fig:arch}. Taking a more detailed look, methods performed by the Twitter
Search Wrapper can be grouped into five sequential steps (see Figure
\ref{fig:arch}) .
>>>>>>> .r181

@@

In a first step the Twitter Search Wrapper fetches the atom feed
generated by the twitter search
api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
query. The generated feed contains information about the 100 most recently published publicly visible tweets and
their authors which match the search query. The tweets itself are described by
their content, publishing date, authors and optionally a geographic location.

In a second (optional) step hyperlinks posted in tweets of the fetched
feed are followed, content of the referenced website's body is fetched and
processed to the Wrapper. This option is triggered calling the Wrapper
service with attribute extern=true.

The Wrapper now calls the Wikifier \cite{key:wikifier} service. Content of the
tweets that matched the search query and optional content of their referenced websites is merged
to a single input string which is used as input for the Wikifier. The service
returns a list of matching articles of the English
Wikipedia. Optionally the wrapper can be initially called with lang=de to
trigger mapping to the German Wikipedia.

The list of matching Wikipedia articles is returned to the Wrapper. The Wrapper
generates a rdf document using popular ontologies (foaf, dublincore,\ldots) to
describe the data related to the returned tweets and their content including 'rdfs:seeAlso' links to
DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted output of the
Wikifier) describing the documents content.

>>>>

The implemented
system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}}
(further called Twitter Search Wrapper) is called with a query representing
the twitter search term and returns a rdf\footnote{\url{http://www.w3.org/RDF/}}
document semantically describing the most recent twitter posts (further called tweets) matching the given query. The returned rdf
document furthermore contains a mapping of the query to Encyclopedia articles
which based on the content published by users that most recently used the search
term in their posts maps to articles best describing the content of tweets
related to the term. An overview of the System Architecture is given in Figure
\ref{fig:arch}. Taking a more detailed look, methods performed by the Twitter
Search Wrapper can be grouped into five sequential steps (see Figure
\ref{fig:arch}) .

@@

In a first step the Twitter Search Wrapper fetches the atom feed
generated by the Twitter Search
API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
query. The generated feed contains the data of the 100 most recently published
publicly visible tweets and their authors which match the search query. The tweets itself are described by
their content, publishing date, authors and optionally a geographic location.

In a second (optional) step hyperlinks posted in tweets of the fetched
feed are followed, content of the referenced website's body is fetched and
processed to the Wrapper. This option is triggered calling the Twitter Search
Wrapper with attribute extern=true.

The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
the tweets that matched the search query and optional content of their referenced websites is merged
to a single input string which is used as input for the Wikifier. The service
returns a list of matching articles of the English
Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
to trigger mapping to the German Wikipedia.

The list of matching Wikipedia articles is finally returned to the Wrapper. The
Wrapper generates a rdf document using popular ontologies (foaf, dublincore, geo) to
describe the data related to the returned tweets and their content using
'rdfs:seeAlso' triples to link the document to
DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted output of the
Wikifier) that have been mapped to the documents content.
